An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-09-18 paper/main.tex
discussion memo

\pgfplotsset{compat=1.12}

@@

@@

\item deadline of PEPM2020 (October 18th)
\item ESOP (?)
\item Need to change the style file of latex..
\item []
\end{itemize}

@@

@@

@@

\begin{itemize}
\item Improvement of evaluation efficiency
  \begin{itemize}
  \item Quadratic to exponential? 
  \item The introduced extentions (maybe) use more memory than the original approach, but they are faster than the original.
  \end{itemize}
\item Tupling is also effective in bidirectional programming.
  \begin{itemize}
  \item A pair of put and get is self-inverse (involution).
  \end{itemize}
\item lazy update \& lazy computation is also good optimization for BX.
%\item Reveal a part of relationship between BX and Reversible.
%  \begin{itemize}
%  \item Very well-behaved (no adaptive-case) \& The same evaluation path $\to$ No garbage Reversible Computation.
%  \item 
%  \item If we can obtain good parameter (dummy) for a BiGUL program,
%    put(s, dummy) can be a complement function.
  \end{itemize}

@@

\begin{itemize}
\item BiGUL papers (PEPM, POPL, tutorial?)
\item the first BX paper
\item view update problem paper
\item get-based 
\end{itemize}

>>>>

\pgfplotsset{compat=1.11}

@@

% plan to pages
% abstraction & title & Introduction: 3pages
% miniBiGUL: 1.5page
% pg: 3pages
% cpg: 2page
% kpg: 1page
% xpg:0.5page
% evaluation:2pages
% related work:1page
% conclusion:1page (including reference)
% page limit : 15

@@

\item deadline of PEPM2020 (October 18th)
\item ESOP (October 24th)
\item FLOPS (the middle of November??)
\item Need to change the style file of latex..
\item []
\end{itemize}

@@

% general, concrete problem
% get-based also have the same problem. even in lenses. more general problem in
% The example should be from lenses.
% traversal, not exactly the same computation

@@

% get & put independently, but for efficient computation
% we need to tuple them to help composition
% 2 or 3 examples to show tupling solves the problem.
% other examples are for showing kpg and cpg is needed.

@@

\begin{itemize}
\item Improvement of evaluation efficiency
  \begin{itemize}
  \item Quadratic to exponential? 
  \item The introduced extentions (maybe) use more memory than the original approach, but they are faster than the original.
  \end{itemize}
\item Get and put more tight

\item (Tupling introduces some constructions)
  \begin{itemize}
  \item A pair of put and get is self-inverse (involution).
  \end{itemize}
\item careful lazyness is needed in our implementation for efficiency
%  lazy update \& lazy computation are also good optimization for BX.
%\item Reveal a part of relationship between BX and Reversible.
%  \begin{itemize}
%  \item Very well-behaved (no adaptive-case) \& The same evaluation path $\to$ No garbage Reversible Computation.
%  \item 
%  \item If we can obtain good parameter (dummy) for a BiGUL program,
%    put(s, dummy) can be a complement function.
  \end{itemize}

@@

\begin{itemize}
%\item BiGUL papers (PEPM, POPL, tutorial?)
%\item the first BX paper
%\item get-based BX
%\item put-based BX?
\item implementation of BX, they might have the same problem, this paper will be first attempt, semantics and correctness is considered more, but efficiency is  lacked.
\item optimization techniques : tupling, lazy computation, fusion transformation?
\item (view update problem paper)
\end{itemize}
